analysis

### 2020-02-17 Trial analyses/explore.Rmd
Move explore markdown to trial analyses folder

```{r}
anova(PM_mv1, L=rbind(c(0,1,-1,0,0), 
                        c(0,0,1,-1,0),
                        c(0,0,1,0,-1),
                        c(0,0,0,-1,1),
                        c(0,1,0,0,1)))
```

@@

results %>%
   filter(treat != "intrcpt") %>% 
   ggplot(aes(treat, mean))+
   geom_point(aes(size = 1/(uci-lci)), shape =15)+
   geom_errorbar(aes(ymin = lci, ymax = uci), width = 0.1)+
   coord_flip()

>>>>

```{r}
PM_mv1

anova(PM_mv1, L=rbind(c(0,1,-1,0,0), 
                        c(0,0,1,-1,0),
                        c(0,0,1,0,-1),
                        c(0,0,0,-1,1),
                        c(0,1,0,0,1)))
```

@@

results$treat <- factor(results$treat, levels = results$treat[c(1,3,5,4,2)])

results %>%
   filter(treat != "intrcpt") %>% 
   ggplot(aes(treat, mean))+
   geom_point(aes(size = 1/(uci-lci)), shape =15)+
   scale_size(name = "1/(upper - lower\nconfidence intervals)")+
   geom_errorbar(aes(ymin = lci, ymax = uci), width = 0.1)+
   scale_x_discrete(labels = c("Late with \n follow spray/s","Recommended with\n follow spray/s","Recommended\n single spray","Early single spray"))+
   labs(y = "Mean yield difference (t/Ha) relative to no spray control",
        x = " ") +
   geom_hline(yintercept = seq(from =  0,to = 0.5, by = 0.1), colour = "grey")+
   coord_flip()+
   theme_usq()
